Wall and LR Fish

### 2024-02-28 Fish Data Analysis/Walls and LR Turns.qmd
Cleaned up code around turns to a set angle
Instead of a rolling average, we now look at the change from the average heading 20 frames before and after a turn

single_fish_turning_step <- stepAIC(single_fish_turning_base, 
                                   list(upper = ~ Wall_Dist*Fish_Num_Ratio, lower = ~1), 
                                   direction = "both",
                                   trace = F)
Anova(single_fish_turning_step)

>>>>

single_fish_turning_step <- stepAIC(single_fish_turning_base, 
                                   list(upper = ~ Wall_Dist*Fish_Num_Ratio, lower = ~1), 
                                   direction = "both",
                                   trace = F)
#Anova(single_fish_turning_step)
